Verifying Demonstrations

### 2018-05-23 paper/analysis-security.tex
Starts editing security analysis

We will start by giving an overview of the protocol.
We have a number of participants.
We have a cothority who provide the storage in a decentralized manner.
The cothority should consist of independent actors, preferably with conflicting 
interests so that they will not collude.
We have Alice the organizer and Bob the participant who are both protesters.
We have the trustworthy journalist Jane who is present but not participating in 
the protest.
The protesters will witness each others participation proofs, \eg Alice will 
witness Bob's proof and Bob will witness Alice's proof.
The result of witnessing a proof is a proof share (essentially a witness 
signature).
Jane will also participate in witnessing the protesters' proofs.
The witnessing is done through local interaction.
As soon as Alice and Bob have departed from the protest they upload their proofs 
(\ie all proof shares) to the cothority for indefinite storage.
Since each proof consists of one proof share for each witness, each witness 
could potentially upload the proof share themselves to the cothority.
This would have the same effect but with added redundancy, in case Alice or Bob 
cannot upload them themselves.

We will now describe the protocol in more details.
We will describe it in the same order as outlined above:
starting with the construction of the participation proof (shares) and 
submitting the proof shares to storage.
Then we will conclude with how to verify the proofs and produce the 
participation count.

@@

An overview of the final structure of a proof is given in \cref{fig:ProofFig} 
and an overview of the communication is given in \cref{fig:ProtocolOverview}.

@@

\Cref{CountOnce} is required to prevent Sybil attacks, \ie that one individual 
can provide two participation proofs and thus be counted twice.
That situation should be detectable.
We can do this by ensuring that Alice cannot produce two valid proofs which
are unlinkable.
\Cref{DesignatedEvent} is to prevent Alice from reusing the same proof (or proof 
share) for another event.
\Eg there might be a counter protest at the same time and place, these would 
have the same spatial and temporal properties.
To distinguish them, we also need to prove for which of these events that a 
proof is designated.
The idea is to construct a unique identifier for a protest.

We will start with the latter.
The identifier of the protest must be regulated, for the same reasons as for the 
user identifiers --- otherwise a counter-protest can simply choose the same 
protest identifier.
As was pointed out in \cref{CauseIsTheCommonDenominator}, the cause is at the 
root of what defines a protest.
The cause can be captured in some sort of \emph{manifesto}, thus, we will use 
the hash value of the manifesto as identifier of the protest (cause).
(As shown as manifesto and cause identifier \(cid\) in \cref{fig:ProofFig}.)

To practically propagate this identifier to the protesters the organizer can 
have a placard with a large QR code that either contains the entire manifesto or 
at least links to a website hosting the manifesto.
The user can scan this QR code with a protesting app which will automatically 
fetch it, show it to the protester for approval and then compute the identifier 
\(cid\).

Next we need to consider the protesters' identifiers to prevent Sybil attacks.
\Citet{HowToWinTheCloneWars} created an \emph{interactive} credential system 
which allows anonymous authentication at most \(n\) times\footnote{%
  Possibly there is another scheme that makes it non-interactive, \eg by 
  \citet{Psignatures}, see issue \#27.
}, where \(n = 1\) in our scenario.
Alice has \iac{PRF} key \(k\) and a blind signature on \(k\) included in her 
national identity-card (by assumption).
She will use \(k\) to compute \(pid\gets \ACprf[_k][cid]\), which is her 
anonymous identity during the protest (shown as \(pid\) in \cref{fig:ProofFig}).

>>>>

@@

@@

\NewVariable{\sk}{sk}

\Cref{CountOnce} is required to prevent Sybil attacks, \ie that one individual 
can provide two participation proofs and thus be counted twice.
This is prevented by the use of \(\pid\).
To be counted twice, Alice must produce a \(\pid'\neq \pid\) and a signature
\begin{align*}
\pi_{\pid'} &= \SPK\mleft\{ (\sk') : \mright. \\
            & \qquad pid = \ACprf[_{\sk'}][cid], \\
            & \qquad \mleft. \sigma = \ACblind[\ACsign[_{ssk}][\sk']] \mright\} 
            \\
            & \qquad\qquad (\cid, \pid', \wid', t_s, t_s', l, wsig').
\end{align*}
\daniel{There are several approaches for Alice to do this, we should describe 
  them.}

\Cref{DesignatedEvent} is to prevent Alice from reusing the same proof (or proof 
share) for another event --- or someone else using her proof-share for another 
event.
This is done with the use of \(\cid\) in the proof shares.
Thus to reuse the proof share for another protest, with a different manifesto, 
one must find a second preimage \(\mfst'\) such that \(\cid = \Hash[\mfst] = 
  \Hash[\mfst']\).
